\LARGE \bf Planning with Attitude

### 2020-10-10 paper/main.tex
Updated flexible sat section.

    Given known vectors in some inertial frame, ${}^N v_i$, and measurements of these
    vectors in some body fixed frame, ${}^B v_i$, our goal is to determine the relative
    rotation from the body to inertial frames ${}^N q^N$, expressed as a quaternion. We
    can define Wahba's loss function as the following: 
    \begin{align} \label{eq:wahba_loss}
        L &= \sum_i w_i \norm{{}^N v_i - {}^N q^B \,\, ^Bv_i }_2^2. = \norm{r_i(q)}_2^2 
    \end{align} 
    where $r_i(q)$ is the residual vector.

@@

    \subsection{Satellite Attitude Keep-Out}
    A spacecraft with flexible appendages modes must perform a 150 degree slew, while ensuring that a star tracker does not look within 40 degrees of the sun. The attitudes that result in the star tracker looking too close to the sun will be referred to as a keep-out zone. The flexible body spacecraft dynamics are based on the truncated hybrid coordinate model, with the three largest modes captured \cite{Tracy2020}. We can guarantee the star tracker body fixed vector ($^Br_{st}$) does not look within 40 degrees of the inertial sun vector ($^Nr_{sun}$) by formulating the following constraint:
    \begin{equation}
        \langle ^N A ^B {}^Br_{st} , ^Nr_{sun}\rangle \leq \cos(40 ^\circ).
    \end{equation}
    Due to this constraint on the feasible attitudes, an eigen-axis slew trajectory planner may end up violating this keep out zone \cite{markley2014fundamentals}. ALTRO can generate a feasible trajectory for this problem since it is able to reason about the nonlinear flexible spacecraft dynamics, actuator constraints, and the star tracker line of sight constraint.
        \begin{figure}
            \centering
            \includegraphics{figures/kevins_plots/attitude_slew_plot.tikz}
            \caption{Visualization of the flexible spacecraft slew with a dedicated keep out zone. Attitude is parameterized with a Rodrigues parameter to visualize in three dimensions. The constraint surface represents attitudes where the star tracker is within 40$^\circ$ of the sun. The unconstrained solution violates this constraint, while the constrained solution is able reason about the keep out zone.}
        \end{figure}

>>>>

    Given known vectors in some inertial frame, ${}^N v_i$, and measurements of these
    vectors in some body fixed frame, ${}^B v_i$, our goal is to determine the relative
    rotation from the body to inertial frames ${}^N q^N$, expressed as a quaternion. We
    can define Wahba's loss function as the following: 
    \begin{align} \label{eq:wahba_loss}
        L &= \sum_i w_i \norm{{}^N v_i - {}^N q^B \,\, ^Bv_i }_2^2 = \norm{r_i(q)}_2^2, 
    \end{align} 
    where $r_i(q)$ is the residual vector.

@@

    \subsection{Satellite Attitude Keep-Out}
    A spacecraft with flexible appendages must perform a 150 degree slew, while ensuring that a star tracker line-of-sight does not cross within 40 degrees of the sun. The attitudes that result in the star tracker pointing too close to the sun will be referred to as a keep-out zone. The flexible body spacecraft dynamics are based on the truncated hybrid coordinate model, with the three largest modes captured \cite{Tracy2020}. We can guarantee the star tracker body fixed vector ($^Br_{st}$) does not look within 40 degrees of the inertial sun vector ($^Nr_{sun}$) by formulating the following constraint:
    \begin{equation}
        \langle ^N q ^B {}^Br_{st} , ^Nr_{sun}\rangle \leq \cos(40 ^\circ).
    \end{equation}
    Due to this constraint on the feasible attitudes, an eigen-axis slew trajectory planner may end up violating this keep-out zone \cite{markley2014fundamentals}. ALTRO can generate a feasible trajectory for this problem since it is able to reason about the nonlinear flexible spacecraft dynamics, actuator constraints, and the star tracker line of sight constraint.
        \begin{figure}
            \centering
            \includegraphics{figures/kevins_plots/attitude_slew_plot.tikz}
            \caption{Visualization of the flexible spacecraft slew with a dedicated keep-out zone. Attitude is parameterized with a Rodrigues parameter to visualize the trajectory in three dimensions. The constraint surface represents attitudes where the star tracker line-of-sight is within 40$^\circ$ of the sun. The unconstrained solution violates this constraint, while the constrained solution is able to avoid the keep out zone.}
        \end{figure}
